---
title: "analysis.rmd"
author: "Amanda Walker"
date: "Thursday, May 28, 2015"
output: html_document
---
#Data analyses and figure creation for Posture and Gravitational Frame experiment

###Amanda Walker and Krista Strother

###Eastern Oregon University, Spring 2015

##Introduction

This is the analyses of raw data collected from [The Effects of Posture on Visualization: A Test of Gravitational Frame of Reference](https://www.youtube.com/watch?v=i9-Vqo_O--o). This is a link directly to the consent form which was recorded on YouTube.  All other materials including the links to assigned conditions and the debriefing are embedded in the previous link.

This data set contains observations from 38 participants.  One participant reported no response to the prompt question, therefore that individual was excluded from this data set.

Although this data set contains three variables (condition, birth month, and side), only the variables condition and side were of interest.  These data were analyzed and displayed in a presentation and on a poster.

##Data Preparation

```{r, echo=FALSE}

dataSet<-read.csv("Raw Data GFR.csv")

```

Observations

```{r, echo=FALSE}

summary(dataSet)

```
Table (Condition and Result)
```{r}

mytable<-table(dataSet$Condition,dataSet$Side)

mytable

```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the figures and analyses.
