---
title: "analysis.Rmd"
author: "Amanda Walker"
date: "Thursday, May 28, 2015"
output: html_document
---
#Data analyses and figure creation for Posture and Gravitational Frame experiment

###Amanda Walker and Krista Strother

###Eastern Oregon University, Spring 2015

##Introduction

This is the analyses of raw data collected from [The Effects of Posture on Visualization: A Test of Gravitational Frame of Reference](https://www.youtube.com/watch?v=i9-Vqo_O--o). This is a link directly to the consent form which was recorded on YouTube.  All other materials including the links to assigned conditions and the debriefing are embedded in the previous link.

This data set contains observations from 38 participants.  One participant reported no response to the prompt question, therefore that individual was excluded from this data set.

Although this data set contains three variables (condition, birth month, and side), only the variables condition and side were of interest.  These data were analyzed and displayed in a presentation and on a poster.

##Data Preparation

```{r, echo=FALSE}

dataSet<-read.csv("Raw Data GFR.csv")

```

Observations

```{r, echo=FALSE}

summary(dataSet)

```
Table (Condition and Result)
```{r}

mytable<-table(dataSet$Condition,dataSet$Side)

mytable

```
##Analysis 

(Chi-Square Test)

```{r}

chisq.test(dataSet$Condition,dataSet$Side)

```

##Results

This test shows no relationship between condition and side, chi squared(1) = 0, p = 1.

This analysis indicates that the side on which a person lies does not influence a visualization task.  Therefore a gravitational frame of reference was not supported in this study.

##Summary

Although some studies indicate posture has effects on various functions (hormonal, biochemical), posture in this study did not seem to affect visualization.  Future research possibilities would include a control for handedness in the sample, visual prompts before the visualization task, and counterbalance for the delivery of response options (Was the ball passed to the left or to the right? versus Was the ball passed to the right or to the left?)


Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the figures and analyses.
